---
title: "p8105_hw5_yh3554"
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(p8105.datasets)
library(viridis)
library(dbplyr)
knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
	fig.width = 8, 
  fig.height = 6,
  out.width = "90%"
)

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d

theme_set(theme_minimal() + theme(legend.position = "bottom"))
```


## Problem 1

First create a dataframe `full_df`that includes all data files from the directory `data/`and complete path to each file. Then use `map` over paths and read data using the `read_csv` function. 

```{r, message = FALSE, warning = FALSE}
full_df = 
  tibble(
    files = list.files("data/"),
    path = str_c("data/", files)
  ) %>% 
  mutate(data = map(path, read_csv)) %>% 
  unnest(cols = c(data))
```

To tidy data dataframe need to use string manipulations on the file, converting from wide to long, and selecting relevant variables. 

```{r}
tidy_df = 
  full_df %>% 
  mutate(
    files = str_replace(files, ".csv", ""),
    group = str_sub(files, 1, 3)) %>% 
  pivot_longer(
    week_1:week_8,
    names_to = "week",
    values_to = "outcome",
    names_prefix = "week_") %>% 
  mutate(week = as.numeric(week)) %>% 
  select(group, subj = files, week, outcome)
```

Creates a plot showing individual data, faceted by group. 

```{r}
tidy_df %>% 
  ggplot(aes(x = week, y = outcome, group = subj, color = group)) + 
  geom_point() + 
  geom_path() + 
  facet_grid(~group)
```

Based on the spaghetti plots, the outcome of experiment group increase over time, but the control group not change much over time. The plots suggest high within-subject correlation -- subjects who start above average end up above average, and those that start below average end up below average.


## Problem 2

#### Read the data

```{r}
homicide_df = read_csv("data_homicide/homicide-data.csv", show_col_types = FALSE)
```

#### Table of proportion of missing data

```{r}
homicide_df %>% 
  summarise_at(vars(lat:disposition), .funs = function(x) mean(is.na(x))) %>%
  knitr::kable()
```

#### Describle the raw data

The `homicide_df` is data contains homicides in 50 large U.S. It has `r nrow(homicide_df)` variables and `r ncol(homicide_df)` cases. The key variables are unique id, victim demographic information (first name, last name, age, sex), the location (city, state, latitude, longitude), and disposition. It has `r sum(is.na (homicide_df$lat))` missing latitude information and `r sum(is.na (homicide_df$lon))` missing longitude information.

#### Generate new dataframe

Create `city_state` variable by combining city and state variales. Then summarize within citries to obtain the total number of homicides and number of unsolved homicides (disposition is “Closed without arrest” or “Open/No arrest”).

```{r}
homicide_tidy <- homicide_df %>% 
  mutate(
    city_state = str_c(city, state, sep = ", ")) %>%
  group_by(city_state) %>%
  summarize(
    homi_tot = n(),
    homi_unsolved = sum(disposition == "Closed without arrest") 
    + sum(disposition == "Open/No arrest" )
  ) %>%
  arrange(desc(homi_tot))

head(homicide_tidy)
```

